Simulating High-Dimensional Multivariate Data

### 2020-11-11 010-background.Rmd
2nd draft. Begin to fix scales, but maybe not needed.

@@

```{r ch010-realDataTab, echo = FALSE, eval=TRUE, message=FALSE, warning=FALSE}
## Describe and plot real data
if ( !file.exists( './data/exampleGenes.rds' ) )  {
    set.seed(10192020)
    exampleGenes <- colnames(brca)[sort(sample(ncol(brca), 3))]
    saveRDS(exampleGenes, file = './data/exampleGenes.rds')
}
exampleGenes <- readRDS('./data/exampleGenes.rds')
knitr::kable(round(head( brca[, exampleGenes], n = 5)),
      booktabs = TRUE,
      caption = 'mRNA counts for three selected high-expressing genes from the first five observations of the BRCA data set.'
)
## GGally::ggpairs(data = as.data.frame(brca[ ,exampleGenes] ))
```

@@

```{r ch010-realDataFig, cache=F, echo = FALSE, eval=TRUE, message=FALSE, warning=FALSE, fig.width= 8, fig.align='center', fig.cap="Marginal scatterplots, densities, and estimated pairwise Spearman's $\rho_s$ for three example genes. The data possess heavy-right tails, are discrete, and have non-trivial intergene correlations. Modeling these data motivate our simulation methodology."}
## Describe and plot real data
## NEED TO CHANGE TO SPEARMANS
GGally::ggpairs(data = as.data.frame(brca[ ,exampleGenes] ))
```

>>>>

```{r ch010-background, echo = FALSE, eval = TRUE, message=FALSE, warning=FALSE, results = "hide", cache=F}
library(tidyverse)
library(GGally)
knitr::opts_chunk$set(echo = FALSE, cache = TRUE)
```

@@

```{r ch010-realDataTab, echo = FALSE, eval=TRUE, message=FALSE, warning=FALSE}
## Describe and plot real data
if ( !file.exists( './data/exampleGenes.rds' ) )  {
    set.seed(10192020)
    exampleGenes <- colnames(brca)[sort(sample(ncol(brca), 3))]
    saveRDS(exampleGenes, file = './data/exampleGenes.rds')
}
exampleGenes <- readRDS('./data/exampleGenes.rds')
small <-  brca %>% select( exampleGenes )
knitr::kable(round(head( small, n = 5)),
      booktabs = TRUE,
      caption = 'mRNA counts for three selected high-expressing genes from the first five observations of the BRCA data set.'
)
```

@@

```{r ch010-realDataFig, cache=F, echo = FALSE, eval=TRUE, message=FALSE, warning=FALSE, fig.width= 8, fig.align='center', fig.cap="Marginal scatterplots, densities, and estimated pairwise Spearman's $\rho_s$ for three example genes. The data possess heavy-right tails, are discrete, and have non-trivial intergene correlations. Modeling these data motivate our simulation methodology."}
# lowerfun <- function(data,mapping){
#   ggplot(data = data, mapping = mapping)+
#     geom_point()+
#     scale_x_continuous(limits = c(-1.5,1.5))+
#     scale_y_continuous(limits = c(-1.5,1.5))
# }

GGally::ggpairs( data = small,
                # lower = list( continuous = wrap(lowerfun)),
                upper = list(
                    continuous = wrap('cor', method = "spearman")
                ), 
                ) + theme_bw()
```
